Sharing displays and data from vision science research with Databrary

### 2015-05-07 vss-15/poster_landscape.tex
modify policies language for accuracy

      Only those with independent researcher status at an institution may apply for authorization. 
      Applicants promise to uphold ethical principles and sign an access agreement co-signed by the institution.

@@

      Identifiable data may only be shared if participants have given permission.
      The Databrary release template may be adapted for specific research protocols.

>>>>

      Only those with independent researcher status at an institution may be granted authorized investigator status.
      Applicants promise to uphold ethical principles and sign an access agreement, which must be co-signed by their institution.

@@

      Identifiable data may only be shared if participants have given permission.
      Databrary has developed a release template for obtaining informed consent for sharing identifiable data.
      The Databrary release template may be adapted for specific research protocols.
